### 2015-12-11 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
another improvement on syntax

 The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  (\isa{Form} or
 \isa{PropForm}) from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
 \isa{Error} or \isa{Term}, then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
 is \isa{Error} and a dummy entity of appropriate type is returned. This illustrates the very 

@@

n-ary lambda abstraction \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
 Metaphysica only for propositional formulas. ... say more about \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
 straightforward: \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
 lambda abstractions, that is, \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} is e.g. mapped to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.

@@

\ lam{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isasymPhi}{\isacharparenright}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline

@@

\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline

@@

We also tried to prove the statement \isa{{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}} with automated reasoners.
 This was however not successful ... (check again and check why).%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%

@@

@@

\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%

@@

\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%

>>>>

 The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  \isa{F} (formula) or
 \isa{P} (propositional formula from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
 \isa{E} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
 is \isa{E} and a dummy entity of appropriate type is returned. This illustrates the very 

@@

n-ary lambda abstraction \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}\isactrlsup {\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
 Metaphysica only for propositional formulas. ... say more about \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
 straightforward: \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
 lambda abstractions, that is, \isa{\isactrlbold {\isasymlambda}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} is mapped to \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} and \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} 
 to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.

@@

\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline

@@

\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline

@@

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x\ y{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}y\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%

@@

\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%

@@

\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
